Put Your Money Where Your Mouth Is: Prediction Markets and Climate Change

### 2016-03-07 paper.Rmd
small paper edits

Traders bet on temperature six years in the future. During the six-year period, traders buy and sell futures. Every year, there is Bayesian updating of traders personal predictions for future temperature based on the current year's temperature. At the end of each six-year period, winners collect money and traders revise beliefs about climate models, based on ideology and beliefs of top earners in their social network. In this section, we describe the models used to generate future temperature data, agents beliefs about those models, the market, and the social network connecting agents. We conclude with details on model dynamics and an overview of the model parameters.

@@

IM GOING TO DELETE THESE 3:
* Timing parameters
    + **burn.in** The number of burn-in periods in which no securities are traded (necessary to allow believed models to be estimated in the first period).
    + **n.seq** Number of trading sequences.
    + **horizon** Number of trading periods in each trading sequence.

>>>>

Traders bet on global temperature anomalies six years in the future. During the six-year period, traders buy and sell futures. Every year, traders update their models and forecast future temperature based on the current year's temperature. At the end of each six-year period, winners collect money and traders revise beliefs about climate models, based on their ideology and the beliefs of top earners in their social network. In this section, we describe the models used to generate future temperature data, agents beliefs about those models, the market procedures, and the social network connecting agents. We conclude with details on model dynamics and an overview of the model parameters.

@@

IM GOING TO DELETE THESE 3 bc we set them:
* Timing parameters
    + **burn.in** The number of burn-in periods in which no securities are traded (necessary to allow believed models to be estimated in the first period).
    + **n.seq** Number of trading sequences.
    + **horizon** Number of trading periods in each trading sequence.
